Improving the Replicability of Psychological Science Through Pedagogy

### 2017-05-17 paper/paper.Rmd
Remover over-powered

header-includes:
   - \usepackage{lscape}

@@

\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllr|lrcl}
  \hline
\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects. * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment. In four cases, we powered the replication attempt to 80\% post-hoc power. In four cases, we used the original sample size. In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

>>>>

header-includes:
   - \usepackage{lscape}
   - \usepackage{multicol}

@@

\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllr|lrcl}
  \hline

 & \multicolumn{5}{c|}{\underline{Original Study}} & \multicolumn{4}{c}{\underline{Replication Study}} \\

\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects. * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment. In four cases, we powered the replication attempt to 80\% post-hoc power. In four cases, we used the original sample size. In one case, the original experiment was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.
